Enhancing Adversarial Robustness for Deep Metric Learning

### 2022-03-02 tab-hmeff.tex
tex
import vishal's changes, part 1
tab

\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
 &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline

@@

CUB & N/A{[}$\mathcal{R}${]} & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
\hline
\multirow{5}{*}{CUB} & ACT{[}$\mathcal{R}${]} & 2 & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
 & ACT{[}$\mathcal{R}${]} & 4 & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
 & ACT{[}$\mathcal{R}${]} & 8 & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
 & ACT{[}$\mathcal{R}${]} & 16 & 28.6 & 38.7 & 15.1 & 43.7 & 15.8 & 37.9 & 16.0 & 31.5 & 0.496 & 0.834 & 11.3 & 9.8 & 21.2 & 2.1 & 34.7\tabularnewline
 & ACT{[}$\mathcal{R}${]} & 32 & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
\hline
\multirow{5}{*}{CUB} & ACT{[}$\mathcal{S}${]} & 2 & 53.0 & 65.1 & 34.7 & 59.9 & 0.0 & 100.0 & 0.0 & 99.8 & 0.877 & 1.637 & 0.0 & 0.0 & 20.4 & 0.0 & 5.1\tabularnewline
 & ACT{[}$\mathcal{S}${]} & 4 & 49.3 & 61.0 & 31.5 & 56.6 & 0.6 & 97.6 & 0.2 & 98.1 & 0.799 & 1.485 & 0.3 & 0.2 & 18.9 & 0.0 & 7.1\tabularnewline
 & ACT{[}$\mathcal{S}${]} & 8 & 42.8 & 54.7 & 26.6 & 53.3 & 4.8 & 72.8 & 2.7 & 73.3 & 0.619 & 1.148 & 8.3 & 4.9 & 23.5 & 0.3 & 18.7\tabularnewline
 & ACT{[}$\mathcal{S}${]} & 16 & 40.5 & 51.6 & 24.8 & 51.7 & 6.7 & 62.1 & 4.9 & 60.6 & 0.566 & 1.014 & 12.4 & 8.6 & 22.5 & 0.9 & 23.7\tabularnewline
 & ACT{[}$\mathcal{S}${]} & 32 & 39.4 & 50.2 & 18.6 & 51.3 & 6.8 & 61.5 & 5.2 & 60.4 & 0.506 & 1.032 & 12.8 & 11.3 & 17.7 & 0.3 & 24.2\tabularnewline
\hline
\multirow{5}{*}{CUB} & HM{[}$\mathcal{R},\mathcal{M}${]} & 2 & 34.3 & 44.9 & 19.5 & 47.4 & 7.7 & 77.5 & 6.5 & 70.8 & 0.636 & 1.281 & 4.3 & 2.6 & 21.1 & 0.2 & 18.1\tabularnewline
 & HM{[}$\mathcal{R},\mathcal{M}${]} & 4 & 30.7 & 40.3 & 16.4 & 45.3 & 13.9 & 60.4 & 13.5 & 48.1 & 0.582 & 1.041 & 6.6 & 6.6 & 20.2 & 1.2 & 27.1\tabularnewline
 & HM{[}$\mathcal{R},\mathcal{M}${]} & 8 & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
 & HM{[}$\mathcal{R},\mathcal{M}${]}  & 16 & 23.8 & 32.6 & 11.6 & 40.6 & 20.9 & 45.0 & 24.6 & 28.6 & 0.494 & 0.805 & 15.6 & 11.3 & 22.1 & 3.2 & 38.0\tabularnewline
 & HM{[}$\mathcal{R},\mathcal{M}${]} & 32 & 23.1 & 31.9 & 11.3 & 40.3 & 22.8 & 46.0 & 24.3 & 28.3 & 0.495 & 0.800 & 14.2 & 11.7 & 19.7 & 3.8 & 38.0\tabularnewline
\hline
\multirow{5}{*}{CUB} & HM{[}$\mathcal{S},\mathcal{M}${]} & 2 & 44.5 & 56.1 & 27.8 & 53.3 & 1.9 & 87.7 & 1.6 & 88.8 & 0.827 & 1.101 & 3.7 & 0.3 & 19.0 & 0.0 & 11.6\tabularnewline
 & HM{[}$\mathcal{S},\mathcal{M}${]} & 4 & 40.6 & 51.8 & 24.2 & 51.0 & 7.3 & 64.1 & 6.3 & 60.9 & 0.715 & 0.894 & 7.9 & 4.4 & 22.8 & 0.2 & 22.1\tabularnewline
 & HM{[}$\mathcal{S},\mathcal{M}${]} & 8 & 38.4 & 49.7 & 22.9 & 50.3 & 10.9 & 50.5 & 10.8 & 44.6 & 0.680 & 0.722 & 13.3 & 11.2 & 25.8 & 1.2 & 29.6\tabularnewline
 & HM{[}$\mathcal{S},\mathcal{M}${]} & 16 & 37.4 & 47.3 & 21.0 & 48.2 & 14.4 & 42.0 & 14.8 & 34.7 & 0.599 & 0.693 & 17.5 & 14.4 & 26.5 & 2.4 & 34.8\tabularnewline
 & HM{[}$\mathcal{S},\mathcal{M}${]} & 32 & 35.3 & 46.1 & 20.2 & 48.0 & 15.1 & 41.8 & 15.2 & 33.0 & 0.589 & 0.686 & 18.7 & 14.9 & 27.8 & 2.9 & 35.7\tabularnewline

@@

}

\caption{Effectiveness of Hardness Manipulation for Adversarial Training.}
\label{tab:hmeff}
\end{table*}

>>>>

\rowcolor{black!12} & & & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \tabularnewline
\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
\rowcolor{black!12}\multirow{-2}{*}{\textbf{Dataset}} & \multirow{-2}{*}{\textbf{Defense}} & \multirow{-2}{*}{$\eta$} & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \multirow{-2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline

@@

CUB & N/A{[}$\mathcal{R}${]} & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
\hline
\multirow{5}{*}{CUB} & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 2 & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
\rowcolor{black!7}\cellcolor{white} & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 4 & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
 & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 8 & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
\rowcolor{black!7}\cellcolor{white} & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 16 & 28.6 & 38.7 & 15.1 & 43.7 & 15.8 & 37.9 & 16.0 & 31.5 & 0.496 & 0.834 & 11.3 & 9.8 & 21.2 & 2.1 & 34.7\tabularnewline
 & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 32 & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
\hline
\multirow{5}{*}{CUB} & \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 2 & 53.0 & 65.1 & 34.7 & 59.9 & 0.0 & 100.0 & 0.0 & 99.8 & 0.877 & 1.637 & 0.0 & 0.0 & 20.4 & 0.0 & 5.1\tabularnewline
\rowcolor{black!7}\cellcolor{white}& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 4 & 49.3 & 61.0 & 31.5 & 56.6 & 0.6 & 97.6 & 0.2 & 98.1 & 0.799 & 1.485 & 0.3 & 0.2 & 18.9 & 0.0 & 7.1\tabularnewline
& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 8 & 42.8 & 54.7 & 26.6 & 53.3 & 4.8 & 72.8 & 2.7 & 73.3 & 0.619 & 1.148 & 8.3 & 4.9 & 23.5 & 0.3 & 18.7\tabularnewline
\rowcolor{black!7}\cellcolor{white}& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 16 & 40.5 & 51.6 & 24.8 & 51.7 & 6.7 & 62.1 & 4.9 & 60.6 & 0.566 & 1.014 & 12.4 & 8.6 & 22.5 & 0.9 & 23.7\tabularnewline
& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 32 & 39.4 & 50.2 & 18.6 & 51.3 & 6.8 & 61.5 & 5.2 & 60.4 & 0.506 & 1.032 & 12.8 & 11.3 & 17.7 & 0.3 & 24.2\tabularnewline
\hline
\multirow{5}{*}{CUB} & HM{[}$\mathcal{R},\mathcal{M}${]} & 2 & 34.3 & 44.9 & 19.5 & 47.4 & 7.7 & 77.5 & 6.5 & 70.8 & 0.636 & 1.281 & 4.3 & 2.6 & 21.1 & 0.2 & 18.1\tabularnewline
\rowcolor{black!7}\cellcolor{white} & HM{[}$\mathcal{R},\mathcal{M}${]} & 4 & 30.7 & 40.3 & 16.4 & 45.3 & 13.9 & 60.4 & 13.5 & 48.1 & 0.582 & 1.041 & 6.6 & 6.6 & 20.2 & 1.2 & 27.1\tabularnewline
 & HM{[}$\mathcal{R},\mathcal{M}${]} & 8 & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
\rowcolor{black!7}\cellcolor{white} & HM{[}$\mathcal{R},\mathcal{M}${]}  & 16 & 23.8 & 32.6 & 11.6 & 40.6 & 20.9 & 45.0 & 24.6 & 28.6 & 0.494 & 0.805 & 15.6 & 11.3 & 22.1 & 3.2 & 38.0\tabularnewline
 & HM{[}$\mathcal{R},\mathcal{M}${]} & 32 & 23.1 & 31.9 & 11.3 & 40.3 & 22.8 & 46.0 & 24.3 & 28.3 & 0.495 & 0.800 & 14.2 & 11.7 & 19.7 & 3.8 & 38.0\tabularnewline
\hline
\multirow{5}{*}{CUB} & HM{[}$\mathcal{S},\mathcal{M}${]} & 2 & 44.5 & 56.1 & 27.8 & 53.3 & 1.9 & 87.7 & 1.6 & 88.8 & 0.827 & 1.101 & 3.7 & 0.3 & 19.0 & 0.0 & 11.6\tabularnewline
\rowcolor{black!7}\cellcolor{white} & HM{[}$\mathcal{S},\mathcal{M}${]} & 4 & 40.6 & 51.8 & 24.2 & 51.0 & 7.3 & 64.1 & 6.3 & 60.9 & 0.715 & 0.894 & 7.9 & 4.4 & 22.8 & 0.2 & 22.1\tabularnewline
 & HM{[}$\mathcal{S},\mathcal{M}${]} & 8 & 38.4 & 49.7 & 22.9 & 50.3 & 10.9 & 50.5 & 10.8 & 44.6 & 0.680 & 0.722 & 13.3 & 11.2 & 25.8 & 1.2 & 29.6\tabularnewline
\rowcolor{black!7}\cellcolor{white} & HM{[}$\mathcal{S},\mathcal{M}${]} & 16 & 37.4 & 47.3 & 21.0 & 48.2 & 14.4 & 42.0 & 14.8 & 34.7 & 0.599 & 0.693 & 17.5 & 14.4 & 26.5 & 2.4 & 34.8\tabularnewline
 & HM{[}$\mathcal{S},\mathcal{M}${]} & 32 & 35.3 & 46.1 & 20.2 & 48.0 & 15.1 & 41.8 & 15.2 & 33.0 & 0.589 & 0.686 & 18.7 & 14.9 & 27.8 & 2.9 & 35.7\tabularnewline

@@

} \vspace{-0.5em}
	%
\caption{Hardness manipulation in adversarial training.
%
The ``$\uparrow$'' mark means ``the higher the better'', while ``$\downarrow$''
	means the opposite.
%
	}
	%
\label{tab:hmeff}
%
\end{table*}
